Visualizing probability distributions across bivariate nonlinear temporal granularities

### 2020-02-17 main.Rmd
uinal, baktun spacing corrected

\begin{equation} \label{eq8}
\begin{split}
C_{uinal, baktun}(z) & = L(C_{uinal, tun}(z) + P(uinal, tun)C_{tun,katun}(z) + C_{uinal, katun}C_{katun, baktun}(z)) \\
              & = L(\lfloor z/20\rfloor \mod 18  +
              20*\lfloor z/20*18\rfloor \mod 20 +
              20*18*20\lfloor z/20*18*20\rfloor \mod 20) \\
\end{split}
\end{equation}

>>>>

\begin{equation} \label{eq8}
\begin{split}
C_{uinal, baktun}(z)  = & L(C_{uinal, tun}(z) + P(uinal, tun)C_{tun,katun}(z) + C_{uinal, katun}C_{katun, baktun}(z)) \\
               = & L(\lfloor z/20\rfloor \mod 18  \\
               &~~~ + 20*\lfloor z/20*18\rfloor \mod 20  \\
               &~~~ + 20*18*20\lfloor z/20*18*20\rfloor \mod 20) \\
\end{split}
\end{equation}
